### 2020-02-28 README.Rmd
updated readme

```{r}
par(mfrow=c(1,2))
zb_plot(zb_doughnut(london_cent, london_area, n_circles = 5), title = "Doughnuts")
zb_plot(zb_segment(london_cent, n_segments = 20), title = "Segments")
zb_plot(zb_zone(london_cent, n_circles = 4, n_segments = 4), title = "Zone with 4 circles and 4 segments")
```

>>>>

```{r fig.height=3}
par(mfrow=c(1,3))
zb_plot(zb_doughnut(london_cent, london_area, n_circles = 5), title = "Doughnuts")
zb_plot(zb_segment(london_cent, n_segments = 20), title = "Segments")
zb_plot(zb_zone(london_cent, n_circles = 4, n_segments = 4), title = "4 segments, 4 circles")
```
